### 2008-05-16 trunk/Papers/dl-gre-08/gre.tex
final version INLG

We presented both algorithms as first refining $\RE$
according to propositional symbols, and then by relational
expressions of increasing depth. But, actually, propositional symbols can be encoded using new relational symbols (e.g., we could represent
that $f_1$ is a flower in Fig.~\ref{fig:dale-haddock} as a relation labeled $\mathsf{flower}$ from $f_1$ to an additional dummy element $d$).
In this way, any
arbitrary ordering of preference can be used when generating $\RE$,
and we don't need to distinguish between propositions and relations.

>>>>

We presented both algorithms as first refining $\RE$ according to
propositional symbols, and then by relational expressions of
increasing depth. But actually, propositional symbols can be encoded
using new relational symbols (e.g., we could represent that $f_1$ is a
flower in Fig.~\ref{fig:dale-haddock} as a relation labeled
$\mathsf{flower}$ from $f_1$ to an additional dummy element $d$).  In
this way, we don't need to distinguish between propositions and
relations, and any arbitrary preference ordering of properties can be
used.
